---
title: "Untitled"
output: html_document
date: "2022-10-12"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
```

## Data 

Imported from: https://nysipm.cornell.edu/eiq/list-pesticide-active-ingredient-eiq-values/

A Method to Measure the Environmental Impact of Pesticides

Table 2: List of Pesticides. Last Updated JAN 2022	

Action:	
IGR = insect growth regulator
PGR = plant growth regulator
PA = plant activator
CP = crop protectant
BP = biopesticides
B = bacteriacide
AC = acaracide
I = insecticide
F = fungicide
H = herbicide
Fum = Soil fumigant
M = Molluscicide 
R = Rodenticide


Missing Data:	
None=no missing data values
B = toxicity to beneficial insects
P = plant surface half life
Z = toxicity to bees
C = chronic health effects
R = runoff potential
L = leaching potential
S = soil residue half life

The formula for determining the EIQ value of individual pesticides is listed below and is the average of the farm worker, consumer, and ecological components.

$$ EIQ={C[(DT*5)+(DT*P)]+[(C*((S+P)/2)*SY)+(L)]+[(F*R)+(D*((S+P)/2)*3)+(Z*P*3)+(B*P*5)]}/3 $$

Formula Symbols:	

DT = Acute dermal toxicity  
D = Toxicity to birds  
F = Toxicity to fish  
Z = Toxicity to bees  
L = Leaching potential  
R = Runoff potential  
S = Soil residue half life  
SY = Mode of action  
C = Chronic health effects 
P = Plant surface health effects  
B = Toxicity to beneficials

Mientras menor sea el valor de EIQ de campo, menor será el impacto ambiental. 

A continuación se muestra una escala de EIQ que sirve de gu í a para clasificar los tratamientos realizados:

Muy bajo: <5
Bajo: 5-25
Medio-alto: 25-45
Muy alto: >45

```{r}
dat <- rio::import("EIQ-values-May_2022.xlsx", skip = 9) %>% 
  janitor::clean_names( )
dat %>% str
```

```{r}
fungi <- dat %>% filter(str_detect(action, "F")) 

fungi %>% pull(common_name)
common_fungicides <- c(
  #DMIs
  "difenoconazole" , "cyproconazole", "epoxiconazole", 
  "propiconazole", "prothioconazole","tebuconazole" ,
  #QoIs
  "azoxystrobin", 
  "picoxystrobin", 
  "pyraclostrobin",
  "trifloxystrobin",
  #SDHI
  "benzovindiflupyr", "fluopyram", "fluxapyroxad" , 
  "sedaxane",
  #Multisites
  "chlorothalonil", 
   "mancozeb",  
  # otros
  "carbendazim", 
  "metalaxyl"
  )
```

```{r}
fungi %>% 
  filter(common_name %in% common_fungicides) %>% 
  arrange(-eiq_value)
```

# References 

- https://agry.um.ac.ir/article_34655.html?lang=en 